---
title: "Spatial Assignment 1 | Group 4"
author: "Alanna Wittet, Jack Halverson, Wladka Kijewska, Yuanzhao Wang"
date: "9/6/2021"
output: html_document
---

## Open Space and Park Lights in Cambridge, MA

This set of maps compares open space and park lights in Cambridge, MA. The 5 maps vary in efficacy, with one notably ineffective example and one very compelling example.

```{r load packages, message=FALSE, echo=FALSE}
library(ggspatial)
library(ggthemes)
library(tidyverse)
library(sf)
```

```{r, echo=FALSE, message=FALSE, results=FALSE}
parklights <- st_read("INFRA_ParkLights.gdb")
openspace <- st_read("RECREATION_OpenSpace.shp")
```

## Map #1
This map clearly shows areas of open space in Cambridge and the concentration of park lights within those open spaces. The opacity of the open space reveals water underneath, which indicates areas where park lights are not expected. Additionally, this map reveals the small set of open spaces that do not have park lights, which may be unpleasant or unsafe.


```{r, echo=FALSE}
ggplot() +
  annotation_map_tile(zoomin = 0, progress = "none", type = "cartolight") +
  geom_sf(data = openspace,
          color = NA,
          alpha = 0.25,
          aes(fill = "Open Space")) +
    geom_sf(data = parklights,
          size = 0.75,      
          shape = 19,
          alpha = 1,
          aes(color = "Park Light")) +
  scale_fill_manual(values = "dark green", name = " ") +
  scale_color_manual(values = "gold", name = "") +
  labs(caption = "Map tiles and data by OpenStreetMap") +
  theme(panel.background = element_rect(fill = "white"),
        legend.key = element_rect(fill = "white"))+
  theme_map() 

```

## Map #2
The "cartodark" basemap may be good in theory to demonstrate the need for park lights at night. The dark basemap shows the data more obviously, but the color scheme is distracting and the points for park lights are too large to distinguish a specific location.


```{R, echo=FALSE}
ggplot() +
  annotation_map_tile(zoomin = 0, progress = "none", type = "cartodark") +
  geom_sf(data = openspace,
          color = NA,
          alpha = 1,
          aes(fill = "Open Space")) +
    geom_sf(data = parklights,
          size = 3,      
          shape = 19,
          alpha = 1,
          aes(color = "Park Light")) +
  scale_fill_manual(values = "blue", name = " ") +
  scale_color_manual(values = "red", name = "") +
  labs(caption = "Map tiles and data by OpenStreetMap") +
  theme(panel.background = element_rect(fill = "white"),
        legend.key = element_rect(fill = "white"))+
  theme_map() 
```